Double-Drift Illusion Boundaries

### 2021-11-19 DoubleDriftResetLimits.Rmd
tried out new data download function in notebook

```{r}
# The functions here allow downloading the collected data from the OSF project:
source('R/data.R')
# This file has some common helper functions:
source('R/common.R')
# The functions in here are used on the data of the bounded tracking experiments:
source('R/tracking_bounded.R')
# And finally some code for the re-tracing experiment...
source('R/retrace_onePass_V4.R')
# As well as models fit to that data:
source('R/models.R')
# Comparison with Sirui Liu's data:
source('R/time.R')
```

@@

```{r}
# from R/data.R
downloadRawData(overwrite=FALSE, experiments=c('bounded_tracking', 'bounded_tracking_V2', 'onePass_V4'))
```

@@

```{r}
retrace <- read.csv('data/onePass_V4/onePass_V4_re-trace.csv', stringsAsFactors = F)
retrace$value <- 1
retrace$value[which(is.na(retrace$boundX))] <- 0
resetcounts <- aggregate(value ~ participant, data=retrace, FUN=sum)
resetcounts$value <- resetcounts$value / (6*6*4)
print(resetcounts)
```

@@

```{r}
resetcountsCOND <- aggregate(value ~ participant + internalspeed + externalspeed, data=retrace, FUN=sum)
print(resetcountsCOND)
hist(resetcountsCOND$value)
```

>>>>

```{r}
# The functions here allow downloading the collected data from the OSF project:
source('R/data.R')
# This file has some common helper functions:
source('R/common.R')
# The functions in here are used on the data of the bounded tracking experiments:
source('R/exp1_tracking.R')
# And finally some code for the re-tracing experiment...
source('R/exp2_retracing.R')
# As well as models fit to that data:
source('R/exp2_models.R')
```

@@

```{r}
# from R/data.R
OSFdata()
```

@@

```{r}
retrace <- read.csv('data/onePass_V4/onePass_V4_re-trace.csv', stringsAsFactors = F)
retrace$value <- 1
retrace$value[which(is.na(retrace$resetX))] <- 0
resetcounts <- aggregate(value ~ participant, data=retrace, FUN=sum)
resetcounts$value <- resetcounts$value / (6*6*4)
print(resetcounts)
#print(mean(retrace$value))
```

@@

```{r}
resetcountsCOND <- aggregate(value ~ participant + abs(internalspeed) + externalspeed, data=retrace, FUN=sum)
print(resetcountsCOND)
hist(resetcountsCOND$value)
```
